### 2025-03-06 README.Rmd
update getting help
add CRAN badges

<!-- badges: start -->
[![R-CMD-check](https://github.com/bmait101/hatchR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/bmait101/hatchR/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

@@

1.  Open a GitHub issue [link here](https://github.com/bmait101/hatchR/issues).
2.  Email the **hatchR** support team ([Morgan Sparks](morgan.sparks@usda.gov), [Bryan Maitland](bryan.maitland@usda.gov))
3.  Post on a support website like Stack Overflow or Cross Validated.

>>>>

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/hatchR)](https://CRAN.R-project.org/package=hatchR)
[![cran checks](https://badges.cranchecks.info/worst/hatchR.svg)](https://cran.r-project.org/web/checks/check_results_hatchR.html)
[![R-CMD-check](https://github.com/bmait101/hatchR/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/bmait101/hatchR/actions/workflows/R-CMD-check.yaml)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
<!-- badges: end -->

@@

1.  Open a GitHub issue [link here](https://github.com/bmait101/hatchR/issues).
2.  Post on a support website like Stack Overflow or Cross Validated.
